\documentclass[12pt, notitlepage]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex

\usepackage{hyperref}
		
%SetFonts

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{tgbonum}

%SetFonts

\title{
	\textbf{
		BIOL 4100-029
	} \\
	\large Undergraduate Research \\
	\large Fall 2021
}

\date{\vspace{-5ex}}

\begin{document}

{\fontfamily{phv}\selectfont %select helvetica (code = phv)

\maketitle

\section{Course Description}
This course focuses on the approaches, techniques, and methodologies required to examine 
plant physiological and terrestrial ecosystem responses and feedbacks to the environment. 
The specific tools taught will be dependent on student interest, 
but may include literature review, experimental design, measurements of plant and soil gas 
exchange and environmental manipulation, regional- and global-scale modeling, 
as well as large data extraction, analysis, and dissemination. The course will focus on
working with the Nutrient Network expriment.

\section{Expected Learning Outcomes and Objectives}
Upon completion of this class, students are expected to be able to:\par
(1)	Read, review, and discuss past and present scientific literature\par
(2) Design a scientific experiment(s)\par
(3) Disseminate scientific ideas\par

\section{Responsibilities of the Student}
Each student is expected to:\par
(1) Perform ~1-2 hours of lab/field work a week\par
(2) Attend the 1-hour small group meeting each week (Thursday at 5 PM)\par
(3) Maintain an electronic journal\par
(4) Adhere to the safety instructions at all times\par
(5) Attend the 1-hour lab meeting each week if your course schedule allows (time TBD)\par

\subsection{Class Time and Location}
Thursdays 5-5:50 PM

Experimental Sciences Building II (ESB II) Room 409 or 
or otherwise agreed upon.

\subsection{Instructor}
Dr. Nick Smith \par
ESB II Room 402D \par
806-834-7363 \par
nick.smith@ttu.edu \par
\textit{Meetings by appointment}

\subsection{Recommended Texts}
Plant Physiological Ecology (2nd Edition; 2008) by Lambers, Chapin, and Pons \par
The book can be accessed from Springer here: 
\url{https://www.springer.com/us/book/9780387783406}. Click on "Access this title on 
SpringerLink." It can also be accessed through the TTU library. \par
Plant Physiology and Development (6th Edition) by Taiz, Ziegler, Moller, and Murphy

\section{Mode of Instruction}
All instruction will be done face-to-face unless the university directs classes be 
taught online (see next section).

\section{Contingency Statement}
If Texas Tech University campus operations are required to change because of health 
concerns related to the COVID-19 pandemic, it is possible that this course will move to 
a fully online delivery format. Should that be necessary, students will need to have 
access to a webcam and microphone for remote delivery of the class. Additionally, students 
will need to have access to Zoom software.

\section{Course Materials}
All course materials, including lecture slides, readings, activities, and code 
will be posted to a GitHub repository for the course.
The primary repository address is
\url{https://github.com/SmithEcophysLab/biol4100_fall2021}.

\section{Attendance Policy}
Attendance is strongly recommended. 
Course assessments will be done during class (see below).

\section{Course Assessment}
\subsection{\textit{Participation and Engagement}}
Being an active and engaged participant in the class will benefit your understanding
of material as well as your peers'. Examples include asking questions, providing feedback,
and facilitating discussion. Participation and engagement of each student will be monitored
during each class period.

\subsection{\textit{Lab journal}}
Every Friday after 4 pm, your electronic lab journal will be checked to ensure that it 
is up-to-date. The content of the lab journal will vary by week. 
Each week, a brief oral report of work done is required. 
In weeks where data is taken, methods, data, and metadata 
should be uploaded to the lab journal. Enough information must be written in the 
laboratory journal to enable independent reproduction and use of the data.

\subsection{\textit{Final report}}
The final report will consist of a project proposal for a project to be carried out 
in a subsequent semester.

\section{Grading}
Participation and Engagement: 50\% \par
Lab journal: 25\% \par
Final report: 25\% \par

\section{Grading Scale}
A: $\geq$ 90\% \par
B: 80 – 90\% \par
C: 70 – 80\% \par
D: 60 – 70\% \par
F: $\leq$ 59.9\% \par

\section{Missing In-class Activities}
Students will be required to be in class to receive participation and engagement points. 
Please read below if class is to be missed due to an officially approved trip, illness, or special circumstance:

\subsection{Officially Approved Trips}
The person responsible for a student representing the University on officially approved 
trips should notify the instructor of the departure and return schedules in advance.  
The student will not be penalized for the absence but is responsible for the material missed.

\subsection{Illness Based Absence Policy}
If at any time during this semester you feel ill, in the interest of your own health and 
safety as well as the health and safety of your instructors and classmates, you are 
encouraged not to attend face-to-face class meetings or events.  Please review the steps 
outlined below that you should follow to ensure your absence for illness will be excused:
\begin{itemize}
	\item{Call Student Health Services at 806.743.2848 or your health care provider.}
	\item{Contact Dr. Smith to let him know of your situation.}
	\item{If appropriate, obtain and return a doctor's note to Dr. Smith.}
\end{itemize}

\subsection{Special Circumstance Absence}
There may be special circumstances that render missing class unavoidable.
If this arises, please let Dr. Smith know of the situation as soon as possible,
so that the loss of point due to the absence can be discussed.

\section{TTU COVID-19 Policy Reminders}
\begin{itemize}
	\item{Although COVID-19 vaccinations are not mandated, Texas Tech is strongly 
	recommending that all students be vaccinated for COVID-19. The vaccines are safe 
	and effective and will protect the student and other members of the Texas Tech community.}
	\item{Masks will not be required for either indoor or outdoor activities on campus, 
	however, all visitors to the Student Health Clinic will be required to wear a mask. 
	The wearing of masks while in public indoor settings and frequently washing your 
	hands has proven to be effective at preventing the spread of COVID-19.}
	\item{The CDC recommends that both vaccinated and unvaccinated individuals 
	wear a face mask indoors after a known exposure.}
	\item{Prior to arrival on campus, all unvaccinated students in university housing 
	should develop an action plan in the event they are required to self-isolate or 
	quarantine due to a positive COVID- 19 diagnosis or exposure. This plan should 
	include a location to complete the self- isolation/quarantine period, access to 
	groceries/meal delivery, access to necessary medications, numbers of emergency 
	contacts, and contact information for their preferred healthcare provider.}
	\item{Fully vaccinated students (including those with medical or religious exemptions) 
	who aren’t experiencing symptoms will not be required to quarantine following an 
	exposure to a COVID-19 positive person, including roommates. Following a known exposure, 
	students should monitor for symptoms over the course of 14 days and quarantine if symptoms develop.}
	\item{Fully vaccinated students who receive a positive diagnosis for COVID-19 will be required to self-isolate. 
	Students that are vaccinated, including those with medical and religious exemptions, 
	and live in university housing will be provided with a location to complete the self-isolation 
	period. If an off-campus location is necessary, the university will cover the associated housing expenses.}
	\item{Unvaccinated or undisclosed students who have been identified as having a known exposure to
	a COVID-19 positive person will be required to quarantine for a minimum of 7 days or 
	longer depending upon testing. If a student is unvaccinated and can prove a COVID-19 
	diagnosis and recovery in the last three months, quarantine will not be required.}
	\item{Unvaccinated or undisclosed students who receive a positive diagnosis for 
	COVID-19 will be required to self-isolate. The university will offer information 
	regarding off-campus options for unvaccinated students that reside in university 
	housing to complete the self-isolation period but will not cover any associated expenses.}
	\item{Any student who has a laboratory confirmed case of COVID-19 must use this link to report:
	\url{https://ttucovid19.ttu.edu/User/Consent}}
	\item{Students who have a high-risk exposure to someone with confirmed or suspected COVID-19 in
	the last 2 weeks should access the online reporting platform to take a “quick assessment” 
	or “full self-screening.” Based on responses, automated messages provide contact 
	information for campus/clinic resources, emergency room precautions, or planning observation.}
	\item{Students who are fully vaccinated and want to participate in the vaccination 
	incentive opportunity may submit their vaccination record to Student Health Services 
	using the Submit Vaccination Record button at \url{https://www.depts.ttu.edu/communications/emergency/coronavirus/}.}
\end{itemize}

COVID-19-related links:
\begin{itemize}
	\item{Student Affair COVID-19 (\url{https://www.depts.ttu.edu/studentaffairs/SACOVID19.php})}
	\item{Student COVID-19 Protocol (\url{https://www.depts.ttu.edu/communications/emergency/coronavirus/provostdocs/Student_COVID-19_Flowchart_07-21-20.pdf})}
	\item{TTU Commitment (\url{https://www.ttu.edu/commitment/})}
\end{itemize}

\section{Special Considerations}
\subsection{Disabling Condition}
Any student who, because of a disability, may require special arrangements in order to 
Any student who, because of a disability, may require special arrangements in order to 
meet the course requirements should contact Dr. Smith as soon as possible to make 
any necessary arrangements. Students should present appropriate verification from Student 
Disability Services. Please note instructors are not 
allowed to provide classroom accommodations to a student until appropriate verification 
from Student Disability Services has been provided. For additional information, you may 
contact the Student Disability Services office at 335 West Hall or 806-742-2405.

\subsection{Religious Holy Days}
"Religious holy day" means a holy day observed by a religion whose places of worship are 
exempt from property taxation under Texas Tax Code §11.20.
A student who intends to observe a religious holy day should make that intention known 
in writing to the instructor prior to the absence. A student who is absent from classes 
for the observance of a religious holy day shall be allowed to take an examination or 
complete an assignment scheduled for that day within a reasonable time after the absence.
A student who is excused may not be penalized for the absence; however, the instructor 
may respond appropriately if the student fails to complete the assignment satisfactorily.

\section{Academic Integrity}
As stated in the Texas Tech University catalog, “The attempt of any students to present 
as their own work that they have not honestly performed is regarded by the faculty and 
administration as a serious offense and renders the offenses liable to serious 
consequences, possibly suspension.” This statement applies to cheating in whatever 
manner, including plagiarism.

\section{TTU Resources for Discrimination, Harassment, and Sexual Violence}
Texas Tech University is committed to providing and strengthening an educational, 
working, and living environment where students, faculty, staff, and visitors are 
free from gender and/or sex discrimination of any kind. Sexual assault, discrimination, 
harassment, and other Title IX violations are not tolerated by the University. 
Report any incidents to the Office for Student Rights and Resolution, 
(806)-742-SAFE (7233) or file a report online at 
\url{titleix.ttu.edu/students}. 

Faculty and staff members at TTU are committed to connecting you to resources on campus. 
Some of these available resources are: 
\begin{itemize}
	\item{TTU Student Counseling Center, 806-742-3674, \url{https://www.depts.ttu.edu/scc}. 
		Provides confidential support on campus.} 
	\item{TTU 24-hour Crisis Helpline, 806-742-5555. 
		Assists students who are experiencing a mental health or interpersonal violence 
		crisis. If you call the helpline, you will speak with a mental health counselor.} 
	\item{Voice of Hope Lubbock Rape Crisis Center, 806-763-7273, 
		\url{https://voiceofhopelubbock.org}.
		24-hour hotline that provides support for survivors of sexual violence.} 
	\item{The Risk, Intervention, Safety and Education (RISE) Office, 806-742-2110, 
		\url{https://www.depts.ttu.edu/rise/}. Provides a range of resources and support 
		options focused on prevention education and student wellness.} 
	\item{Texas Tech Police Department, 806-742-3931, 
		\url{http://www.depts.ttu.edu/ttpd/}. 
		To report criminal activity that occurs on or near Texas Tech campus.}
\end{itemize}

\section{LGBTQIA}
I, Dr. Smith, identify as an ally to the lesbian, gay, bisexual, transgender, queer, intersex, 
and asexual (LGBTQIA) community, and I am available to listen and support you in an 
affirming manner. I can assist in connecting you with resources on campus to address 
problems you may face pertaining to sexual orientation and/or gender identity that could 
interfere with your success at Texas Tech. Please note that additional resources are 
available through the Office of LGBTQIA within the Center for Campus Life, 
Student Union Building Room 201, 
\url{www.lgbtqia.ttu.edu}, 806.742.5433.

\section{Online Classroom Civility}
Texas Tech University is a community of faculty, students, and staff sharing an 
expectation of cooperation, professionalism, respect and civility in all forms of 
university communication and business. This expectation applies to all interactions in a 
classroom setting where an exchange of ideas and creative thinking should be encouraged 
and where intellectual growth and development are fostered. As we consider ways in which 
we maintain a productive and cooperative online environment, many of the same standards 
from a face-to-face instruction transfer to the online setting. In this way, at the 
instructor’s discretion, disruptive behavior may result in disciplinary referrals pursuant 
to the Texas Tech University Code of Student Conduct. Students are expected to maintain 
online behaviors that are conducive to learning.

Examples of behavior that may be considered disruptive include:
\begin{itemize}
	\item{Disrupting the flow of a class session(s) by making off-topic comments.}
	\item{Enabling or participating in online classroom hijacking (“Zoombombing”) by 
	participating in online classroom streams without being enrolled in the course or 
	by sharing streaming classroom links with parties not enrolled in the course.}
	\item{Spamming, hacking, or using TTU or Blackboard platforms for commercial purposes.}
	\item{Cyberbullying or online harassment.}
	\item{Habitually interfering with or stopping instructional delivery}
\end{itemize}

\section{Creating Livable Futures}
This class is part of a campus-wide initiative called Creating Livable Futures, 
which is sponsored in part by the Texas Tech Center for Global Communication. 
As such, one of our objectives is to prepare you to communicate, 
in a fully interdisciplinary and global way, the challenges posed by pressing issues 
that speak to our collective wellbeing and sustainability. You will be asked to translate 
and communicate the work of leading thinkers on sustainability, and to expand discussing 
those materials through research experience and experiential learning.
These objectives will be met through discussion leads and the review paper. 

Your progress in communicating about global issues will be evaluated according to the 
Center for Global Communication rubric, so you will be invited to participate 
in one or more Creating Livable Futures activities outside of class that will 
complement class content. 
Planned Creating Livable Futures activities include participating in and attending 
speaker events and conferences, edit-a-thons, blogging and publication opportunities, 
student organizations, a book club, and even small scholarship opportunities for research. 

You’ll be informed of relevant opportunities and activities as they arise over 
the course of the semester.

\newpage

\section*{Schedule of Topics by Week}
25/08/21 – Introductions, semester planning, and goals \par
01/09/21 – Plants and ecosystem services \par
08/09/21 – Introduction to the Nutrient Network \par
15/09/21 – Nutrient Network visit and sampling \par
22/09/21 – Eutrophication and biomass \par
29/09/21 – Eutrophication and plant diversity \par
06/10/21 – Eutrophication and leaf traits \par
13/10/21 – Eutrophication and gas exchange \par
20/10/21 – Eutrophication and herbivory \par
27/10/21 – Eutrophication and soil processes \par
03/11/21 – NO CLASS \par
10/11/21 – Proposal writing brainstorm \par
17/11/21 – Proposal writing workshop \par
24/11/21 – NO CLASS \par
01/12/21 – Proposal presentations \par

} %end font selection

\end{document} 
